Output Summary

### 2022-01-11 03-post-process/output-plots.Rmd
Update more variable names
This time, done throughout all files

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# Probability of Maturing at Age-3
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1_Rb[origin,pop]", "sig_Lpsi_O1_Rb[origin,pop]", "rho_Lpsi_O1_Rb[.,.,origin]", "psi_O1_Rb[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O1_Rb_diags = rbind(tmp1, tmp2)

# Probability of Maturing at Age-4
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2_Rb[origin,pop]", "sig_Lpsi_O2_Rb[origin,pop]", "rho_Lpsi_O1_Rb[.,.,origin]", "psi_O2_Rb[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O2_Rb_diags = rbind(tmp1, tmp2)

@@

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
base = c("O_phi_scaler_nat_hat[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# Straying
L1 = "Strays"
L2 = c("Realized Number", "Age Comp")
match = c("n_stray_tot[.+,.]", sub_index("stray_comp[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
stray_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

# weir composition
new = post_subset(post, "weir_x_obs_new_dev", TRUE)
obs = post_subset(post, "weir_x_obs_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
bp[jags_data$weir_nx_obs == 0 | is.na(jags_data$weir_nx_obs)] = NA
weir_x_bp = data.frame(
  name = rep("Weir", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(weir_x_bp) = NULL

# carcass composition
new = post_subset(post, "carc_x_obs_new_dev", TRUE)
obs = post_subset(post, "carc_x_obs_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
bp[jags_data$carc_nx_obs == 0 | is.na(jags_data$carc_nx_obs)] = NA
carc_x_bp = data.frame(
  name = rep("Carcasses", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(carc_x_bp) = NULL

# pre-spawn survival
new = post_subset(post, "carcs_spawned_new_dev", TRUE)
obs = post_subset(post, "carcs_spawned_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
carcs_spawned_bp = data.frame(
  name = rep("Prespawn", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(carcs_spawned_bp) = NULL

# movement survival from BON to LGR
new = post_subset(post, "LGR_adults_new_dev", TRUE)
obs = post_subset(post, "LGR_adults_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
LGR_adults_bp = data.frame(
  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(LGR_adults_bp) = NULL

### COMBINE INTO ONE TABLE ###
bp_tab = rbind(
  Pa_bp, Mb_bp, Ra_bp,
  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
  phi_Ma_O0_bp, weir_x_bp, carc_x_bp, carcs_spawned_bp, LGR_adults_bp
)

@@

  out = list(
    egg_to_parr_surv = post_summ(post, sub_index("^Lphi_E_Pb_resid[.+,pop]", pop = j))["mean",],
    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_Rb_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
  )
  out = do.call(cbind, out)
  rownames(out) = NULL
  out
}
```

@@

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_nor], jags_data$BON_adults[observable,o_nor] - jags_data$LGR_adults[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$LGR_adults[observable,o_hor], jags_data$BON_adults[observable,o_hor] - jags_data$LGR_adults[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r calculate-aggregated-comps-model}
# extract the full posteriors of the two composition sets
q_Ra_full = post_subset(post, "q_Ra", matrix = TRUE)
q_Sa_adj_full = post_subset(post, "q_Sa", matrix = TRUE)

# primary containers: will store final recalculated output
q_Ra_age = q_Sa_adj_age = q_Ra_origin = q_Sa_adj_origin = NULL

@@

  # format the posterior draw as arrays -- easier to subset
  q_Ra = array_format(q_Ra_full[i,])
  q_Sa_adj = array_format(q_Sa_adj_full[i,])

@@

  # containers
  q_Ra_age_tmp = q_Sa_adj_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
  inds_1_age = inds_2_age = inds_3_age = q_Ra_age_tmp
  for (j in 1:jags_data$nj) {
    for (k in 1:jags_data$nk) {
      # calculate aggregate proportions for each age
      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,ko_age[[k]],j])
      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,ko_age[[k]],j])

@@

  # vectorize, add names, and remove NAs
  q_Ra_age_v = as.numeric(q_Ra_age_tmp)
  q_Sa_adj_age_v = as.numeric(q_Sa_adj_age_tmp)
  names(q_Ra_age_v) = paste0("q_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  names(q_Sa_adj_age_v) = paste0("q_Sa_adj_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  q_Ra_age_v = q_Ra_age_v[!is.na(q_Ra_age_v)]
  q_Sa_adj_age_v = q_Sa_adj_age_v[!is.na(q_Sa_adj_age_v)]

@@

  # containers
  q_Ra_origin_tmp = q_Sa_adj_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
  inds_1_origin = inds_2_origin = inds_3_origin = q_Ra_origin_tmp
  for (j in 1:jags_data$nj) {
    for (o in 1:jags_data$no) {
      # calculate aggregate proportions for each origin
      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,ko_origin[[o]],j])
      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,ko_origin[[o]],j])

@@

  # vectorize, add names, and remove NAs
  q_Ra_origin_v = as.numeric(q_Ra_origin_tmp)
  q_Sa_adj_origin_v = as.numeric(q_Sa_adj_origin_tmp)
  names(q_Ra_origin_v) = paste0("q_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  names(q_Sa_adj_origin_v) = paste0("q_Sa_adj_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  q_Ra_origin_v = q_Ra_origin_v[!is.na(q_Ra_origin_v)]
  q_Sa_adj_origin_v = q_Sa_adj_origin_v[!is.na(q_Sa_adj_origin_v)]

@@

  q_Ra_age = rbind(q_Ra_age, q_Ra_age_v)
  q_Sa_adj_age = rbind(q_Sa_adj_age, q_Sa_adj_age_v)
  q_Ra_origin = rbind(q_Ra_origin, q_Ra_origin_v)
  q_Sa_adj_origin = rbind(q_Sa_adj_origin, q_Sa_adj_origin_v)

@@

# combine new calculated quantities into a big matrix
q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_origin, q_Sa_adj_origin)

@@

# containers
x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))

for (j in 1:jags_data$nj) {
  # calculate aggregate proportions for each age
  for (k in 1:jags_data$nk) {
    x_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,ko_age[[k]],j])
    x_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,ko_age[[k]],j])
  }

  # calculate aggregate proportions for each origin
  for (o in 1:jags_data$no) {
    x_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,ko_origin[[o]],j])
    x_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,ko_origin[[o]],j])
  }
}

dimnames(x_weir_age_obs)[[1]] = dimnames(x_weir_origin_obs)[[1]] = dimnames(x_carc_age_obs)[[1]] = dimnames(x_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]

x_weir_new_obs = list(
  x_weir_age_obs = x_weir_age_obs,
  x_weir_origin_obs = x_weir_origin_obs
)

x_carc_new_obs = list(
  x_carc_age_obs = x_carc_age_obs,
  x_carc_origin_obs = x_carc_origin_obs
)

@@

# for multinomial sample size
weir_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$weir_nx_obs[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$weir_nx_obs[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$weir_nx_obs[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

@@

  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

@@

# extract posterior samples of the slope parameter
beta_per = post_subset(post, "mu_beta_per_wul", TRUE)

>>>>

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
match = c("alpha", "^beta[", "lambda", "sig_lbeta", "sig_Lphi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# Probability of Maturing at Age-3
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O1[origin,pop]", "sig_Lpsi_O1[origin,pop]", "rho_Lpsi_O1[.,.,origin]", "psi_O1[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O1_diags = rbind(tmp1, tmp2)

# Probability of Maturing at Age-4
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Among-pop Correlation", "Realized")
base = c("mu_psi_O2[origin,pop]", "sig_Lpsi_O2[origin,pop]", "rho_Lpsi_O2[.,.,origin]", "psi_O2[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O2_diags = rbind(tmp1, tmp2)

@@

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
base = c("delta[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# Straying
L1 = "Strays"
L2 = c("Realized Total Number", "Age Comp")
match = c(sub_index("G[.,origin,pop]", origin = o_hor, pop = "."), sub_index("p_G[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
G_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_diags,
  psi_O2_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  G_diags
)

@@

# weir composition
new = post_subset(post, "x_Ra_new_dev", TRUE)
obs = post_subset(post, "x_Ra_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
bp[jags_data$nx_Ra == 0 | is.na(jags_data$nx_Ra)] = NA
x_Ra_bp = data.frame(
  name = rep("Weir", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(x_Ra_bp) = NULL

# carcass composition
new = post_subset(post, "x_Sa_prime_new_dev", TRUE)
obs = post_subset(post, "x_Sa_prime_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
bp[jags_data$nx_Sa_prime == 0 | is.na(jags_data$nx_Sa_prime)] = NA
x_Sa_prime_bp = data.frame(
  name = rep("Carcasses", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(x_Sa_prime_bp) = NULL

# pre-spawn survival
new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
x_carcass_spawned_bp = data.frame(
  name = rep("Prespawn", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(x_carcass_spawned_bp) = NULL

# movement survival from BON to LGR
new = post_subset(post, "x_LGR_new_dev", TRUE)
obs = post_subset(post, "x_LGR_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
x_LGR_bp = data.frame(
  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(x_LGR_bp) = NULL

### COMBINE INTO ONE TABLE ###
bp_tab = rbind(
  Pa_bp, Mb_bp, Ra_bp,
  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
  phi_Ma_O0_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
)

@@

  out = list(
    egg_to_parr_surv = post_summ(post, sub_index("^Lphi_E_Pb_resid[.+,pop]", pop = j))["mean",],
    p_fall_mig = post_summ(post, sub_index("^Lpi_resid[.+,pop]", pop = j))["mean",],
    ow_surv_fall = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 1))["mean",],
    ow_surv_spring = post_summ(post, sub_index("^Lphi_Pa_Mb_resid[.+,LH_type,pop]", pop = j, LH_type = 2))["mean",],
    toLGR_surv_nor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 1))["mean",],
    toLGR_surv_hor = post_summ(post, sub_index("^Lphi_Mb_Ma_resid[.+,origin,pop]", pop = j, LH_type = 2, origin = 2))["mean",],
    LGR_to_BON_surv_nor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 1))["mean",],
    LGR_to_BON_surv_hor = post_summ(post, sub_index("^Lphi_Ma_O0_resid[.+,origin]", origin = 2))["mean",],
    yr1_ocean_surv = post_summ(post, sub_index("^Lphi_O0_O1_resid[.+,1,pop]", pop = j))["mean",-1],
    age3_mat_nor = post_summ(post, sub_index("^Lpsi_O1_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age3_mat_hor = post_summ(post, sub_index("^Lpsi_O1_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    age4_mat_nor = post_summ(post, sub_index("^Lpsi_O2_resid[.+,origin,pop]", origin = 1, pop = j))["mean",],
    age4_mat_hor = post_summ(post, sub_index("^Lpsi_O2_resid[.+,origin,pop]", origin = 2, pop = j))["mean",],
    BON_to_LGR_surv_nor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 1))["mean",],
    BON_to_LGR_surv_hor = post_summ(post, sub_index("^Lphi_Rb_Ra_resid[.+,origin]", origin = 2))["mean",],
    prespawn_surv = post_summ(post, sub_index("Lphi_Sb_Sa_resid[.+,pop]", pop = j))["mean",]
  )
  out = do.call(cbind, out)
  rownames(out) = NULL
  out
}
```

@@

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

```{r calculate-aggregated-comps-model}
# extract the full posteriors of the two composition sets
p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)

# primary containers: will store final recalculated output
p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL

@@

  # format the posterior draw as arrays -- easier to subset
  p_Ra = array_format(p_Ra_full[i,])
  p_Sa_prime = array_format(p_Sa_prime_full[i,])

@@

  # containers
  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
  for (j in 1:jags_data$nj) {
    for (k in 1:jags_data$nk) {
      # calculate aggregate proportions for each age
      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])

@@

  # vectorize, add names, and remove NAs
  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]

@@

  # containers
  p_Ra_origin_tmp = p_Sa_prime_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
  inds_1_origin = inds_2_origin = inds_3_origin = p_Ra_origin_tmp
  for (j in 1:jags_data$nj) {
    for (o in 1:jags_data$no) {
      # calculate aggregate proportions for each origin
      p_Ra_origin_tmp[,o,j] = rowSums(p_Ra[,ko_origin[[o]],j])
      p_Sa_prime_origin_tmp[,o,j] = rowSums(p_Sa_prime[,ko_origin[[o]],j])

@@

  # vectorize, add names, and remove NAs
  p_Ra_origin_v = as.numeric(p_Ra_origin_tmp)
  p_Sa_prime_origin_v = as.numeric(p_Sa_prime_origin_tmp)
  names(p_Ra_origin_v) = paste0("p_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  names(p_Sa_prime_origin_v) = paste0("p_Sa_prime_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  p_Ra_origin_v = p_Ra_origin_v[!is.na(p_Ra_origin_v)]
  p_Sa_prime_origin_v = p_Sa_prime_origin_v[!is.na(p_Sa_prime_origin_v)]

@@

  p_Ra_age = rbind(p_Ra_age, p_Ra_age_v)
  p_Sa_prime_age = rbind(p_Sa_prime_age, p_Sa_prime_age_v)
  p_Ra_origin = rbind(p_Ra_origin, p_Ra_origin_v)
  p_Sa_prime_origin = rbind(p_Sa_prime_origin, p_Sa_prime_origin_v)

@@

# combine new calculated quantities into a big matrix
q_new = cbind(p_Ra_age, p_Sa_prime_age, p_Ra_origin, p_Sa_prime_origin)

@@

# containers
x_Ra_age_obs = x_Sa_prime_age_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$nk, jags_data$nj))
x_Ra_origin_obs = x_Sa_prime_origin_obs = array(NA, dim = c(jags_data$ny_obs, jags_data$no, jags_data$nj))

for (j in 1:jags_data$nj) {
  # calculate aggregate proportions for each age
  for (k in 1:jags_data$nk) {
    x_Ra_age_obs[,k,j] = rowSums(jags_data$x_Ra[,ko_age[[k]],j])
    x_Sa_prime_age_obs[,k,j] = rowSums(jags_data$x_Sa_prime[,ko_age[[k]],j])
  }

  # calculate aggregate proportions for each origin
  for (o in 1:jags_data$no) {
    x_Ra_origin_obs[,o,j] = rowSums(jags_data$x_Ra[,ko_origin[[o]],j])
    x_Sa_prime_origin_obs[,o,j] = rowSums(jags_data$x_Sa_prime[,ko_origin[[o]],j])
  }
}

dimnames(x_Ra_age_obs)[[1]] = dimnames(x_Ra_origin_obs)[[1]] = dimnames(x_Sa_prime_age_obs)[[1]] = dimnames(x_Sa_prime_origin_obs)[[1]] = dimnames(jags_data$x_Ra)[[1]]

x_Ra_new_obs = list(
  x_Ra_age_obs = x_Ra_age_obs,
  x_Ra_origin_obs = x_Ra_origin_obs
)

x_Sa_prime_new_obs = list(
  x_Sa_prime_age_obs = x_Sa_prime_age_obs,
  x_Sa_prime_origin_obs = x_Sa_prime_origin_obs
)

@@

# for multinomial sample size
weir_sample_size = function(j) {
  par(mar = c(3,3,1.5,0.5), tcl = -0.15, mgp = c(2,0.35,0))
  mp = barplot(jags_data$nx_Ra[observable,j], xaxt = "n", col = alpha("skyblue2", 0.5), border = "blue",
               ylim = c(0, max(jags_data$nx_Ra[observable,j], na.rm = TRUE)),
               xlab = "Return Year", ylab = "Adults at Weir Sampled for Composition")
  usr = par("usr")
  at_x = seq(1, length(observable), 4)
  axis(side = 1, at = mp[at_x], labels = substr(names(jags_data$nx_Ra[observable,j]), 3, 4)[at_x])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
}

@@

  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 1), main = TeX("$NOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Ra_origin[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(x_Ra_new_obs$x_Ra_origin_obs[observable,,j], 2), main = TeX("$HOR$"), ylim = c(0,1), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

@@

# extract posterior samples of the slope parameter
beta_per = post_subset(post, "lambda", TRUE)
